Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 PandaEvolution.tex

Detector simulation is part of the ATLAS production Monte Carlo (MC) workflow
(also known as MC production
chain)~\cite{rimoldi2006atlas,de2013delphes,ritsch2014atlas}. The MC workflow
consists of four main stages: event generation, detector simulation,
digitization, and reconstruction. Event generation creates sets of particle
four-momenta via different generators, e.g., PYTHIA~\cite{sjostrand2006pythia},
HERWIG~\cite{corcella2001herwig} and many others. \mtnote{Addresses Alexei's comment. Is the following sentence correct?} The detector simulator is
called Geant4~\cite{agostinelli2003geant4} and simulates both the ATLAS detector and it's interaction physical processes.
% the interaction of these particles with the sensitive material of the ATLAS
% detector.
Each interaction creates a so-called hit and all hits are collected and passed
on for digitalization where hits are further process to mimic the readout of the
detector. Finally, reconstruction operates local pattern recognition, creating
high-level objects like particles and jets.

@@

\mtnote{Please feel free to add details about backfill as needed.}
\mtnote{Please note: I know the following departs for the current name given to
the PanDA subsystem installed on Titan. I think there is a good reason to call
it a broker instead of a pilot, and I think I explained it in the previous
paragraphs. Please  take this just as a suggestion, something I would like to
discuss in our meeting.} \sergeynote{It's not a pilot in conventional sense. I
call it an agent. It just happened that we were able to use full PanDA pilot's
code base to serve our purposes on Titan. that's why, by inertia, we still call
it a pilot.}\mtnote{Thank you. We would have a problem calling it `agent' as we
use that term to name the pilot of NGE. Would PanDA Broker work?}\sergeynote{OK
broker it is for this paper.}

>>>>

Detector simulation is part of the ATLAS production Monte Carlo (MC) workflow
(also known as MC production
chain)~\cite{rimoldi2006atlas,de2013delphes,ritsch2014atlas}. The MC workflow
consists of four main stages: event generation, detector simulation,
digitization, and reconstruction. Event generation creates sets of particle
four-momenta via different generators, e.g., PYTHIA~\cite{sjostrand2006pythia},
HERWIG~\cite{corcella2001herwig} and many others. \mtnote{Addresses Alexei's
comment. Is the following sentence correct?} The detector simulator is called
Geant4~\cite{agostinelli2003geant4} and simulates the ATLAS detector and the
interaction between that detector and particles.
% the interaction of these particles with the sensitive material of the ATLAS
% detector.
Each interaction creates a so-called hit and all hits are collected and passed
on for digitalization, where hits are further process to mimic the readout of
the detector. Finally, reconstruction operates local pattern recognition,
creating high-level objects like particles and jets.

@@

% \mtnote{Please feel free to add details about backfill as needed.}
% \mtnote{Please note: I know the following departs for the current name given
% to the PanDA subsystem installed on Titan. I think there is a good reason to
% call it a broker instead of a pilot, and I think I explained it in the
% previous paragraphs. Please  take this just as a suggestion, something I would
% like to discuss in our meeting.} \sergeynote{It's not a pilot in conventional
% sense. I call it an agent. It just happened that we were able to use full
% PanDA pilot's code base to serve our purposes on Titan. that's why, by
% inertia, we still call it a pilot.}\mtnote{Thank you. We would have a problem
% calling it `agent' as we use that term to name the pilot of NGE. Would PanDA
% Broker work?}\sergeynote{OK broker it is for this paper.}
